\documentclass[../../main/main.tex]{subfiles}

\begin{document}

\subsection*{From Louvain to Leiden: guaranteeing well-connected communities}

Traag et al.~\cite{traag19-03} proposes a new algorithm for community detection that improves connectedness.
In particular, they show that compared to the Louvain algorithm, it has better accuracy.
Moreover, they prove theoretical guarantes about the connectedness of the output.

First, they describe modularity, an objective function which is given by the formula
$$
	\mathscr{H} = \frac{1}{2m} \sum_c \left( m_c - \gamma \frac{K_c^2}{2m} \right)
$$
where $c$ denotes a community, $m$ the edges and $K$ the sum of degrees.
Note that the expected number of edges in a community is $\frac{K_c^2}{2m}$, so the algorithm maximizes differences between the expected and actual.
Higher resolutions ($\gamma$) lead to more communities, while lower resolutions lead to fewer.

Similarly, the Constant Potts Model (CPM) is given by
$$
	\mathscr{H} = \sum_c \left( m_c - \gamma \frac{n_c}{2} \right)
$$
The density within and between communities are separated by the threshhold $\gamma$.

For both models, higher resolutions lead to more communities, while lower resolutions lead to fewer.
TODO: explain why.

The Louvain algorithm~\cite{blondel08-10} maximizes Modularity or CPM in by repeating two stages.
\begin{enumerate}
	\item Local moving of nodes
	\item Aggregation of the network
\end{enumerate}
Stage I is a greedy step: move each vertex into the community s.t. maximizing the increase in score.
Stage II then collapses each communities into a nodes.
The algorithm runs until convergence (when Step I does nothing).
At this point, merging two communities never increases the score, and neither does moving a node.

First, they show a pathological example of when Lovain produces a disconnected cluster.
Suppose we have clusters $c_1$ and $c_2$, with vertex $v$ a vertex cut in $c_1$.
Then, because of the independent movement, $v$ can be moved into $c_2$ and so disconnecting $c_1$.
Moreover, the more connected $c_1$ is, the less likely it is for it to be split.
TODO: find a better example than this

The Leiden algorithm introduces an additional step of \emph{refining} the partition $\mathcal{P}$.
$\mathcal{P}_{\text{refined}}$ is created in the following way:
\begin{enumerate}
	\setcounter{enumi}{-1}
	\item $i = 0$, and $P_i$ is the singleton partition
	\item For each community in $\mathcal{P}$,
	\item \begin{enumerate}
		      \item For each node, consider all communities in $P_i \big|_\mathcal{P}$ s.t. the objective increase
		      \item Pick a community uniformly and merge
	      \end{enumerate}
	\item Increment $i$, go to 1.
\end{enumerate}

\bibsub

\end{document}

